---
title: "Task1"
author: "Nikita Sheliakov"
date: "10/01/2024"
format:
  html:
    embed-resources: true
editor: source
---

## Question 1

Question description

```{r}
# code for solving task
v1 <- 10.62636237
v2 <- 40L
v3 <- "character variable skjdhfkjshadfjksdhf"
v4 <- TRUE
v5 <- 16+8i 
print(c(v1,v2,v3,v4,v5))
```


## Question 2

Question description
2. Create the next vectors:
  * sequence from 5 to 75;
  * numbers: 3.14, 2.71, 0, 13;
  * with 100 `TRUE` values.
```{r}
# code for solving task
sequence_vektor <- 5:75
number_vector <- c(3.14,2.71,0.13)
true_vector <- rep(TRUE,100)

sequence_vektor
number_vector
true_vector
```

## Question 3

Question description
3. Create the next matrix:

|  |   |  |
|:---:|:-----:|:---:|
| 12  | 34    | 87  |
| -12 | -12.1 | 0   |
| 3.6 | 0.5   | 1.3 |
```{r}
# code for solving task
my_data <- matrix(c(12, 34, 87, -12, -12.1, 0, 3.6, 0.5, 1.3), nrow = 3, byrow = TRUE)
print(my_data)
```

## Question 4
Question description
4. Create a 'list' with all atomic types.
```{r}
# code for solving task
my_list <- list(
  integer_value = 75L,
  numeric_value = 5.43,
  character_value = "Have a good day",
  logical_value = TRUE, 
  complex_value = 2+4i
)

my_list  
```

## Question 5
Question description
5. Create a 'factor' with 3 levels: 'infant', 'child', 'adult'.
```{r}
# code for solving task
my_factor <- factor(c("big", "avarage", "small", "small", "avarage", "big"),
levels = c("big", "avarage", "small"))
my_factor
```

## Question 6
Question description
6. Create a 'data frame'
```{r}
# code for solving task
age_factor <- factor(c("infant", "child", "adult"), levels = c("infant", "child", "adult"))
print(age_factor)
```

## Question 7
Question description
Change column names of the 'date frame'
```{r}
names(my_data) <- c("V4 country", "population, M")
my_data
```

